---
title: "final_project_women_politics"
date: "2020/6/21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(httr)
library(rvest) 
options(stringsAsFactors = F)
```

# 2019
```{r}
url_19 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif010119.htm"
w_19 <- read_html(url_19) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()
w_19 <- as.data.frame(w_19)
w_19 <- w_19[(5:197),]

w_19 <- as.data.frame(w_19) %>%
  mutate(id = row_number())
w_19$w_19 <- gsub(" [0-9]+", "",w_19$w_19)

r_19 <- read_html(url_19) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()
r_19 <- as.data.frame(r_19)
r_19 <- r_19[(2:194),]

r_19 <- as.data.frame(r_19) %>%
  mutate(id = row_number())

t_19 <- merge(w_19,r_19,by = "id")
t_19[1] <- NULL
```
# 2018
```{r}
url_18 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif010118.htm"
w_18 <- read_html(url_18) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()
w_18 <- as.data.frame(w_18)
w_18 <- w_18[(5:197),]

w_18 <- as.data.frame(w_18) %>%
  mutate(id = row_number())
w_18$w_18 <- gsub(" [0-9]+", "",w_18$w_18)

r_18 <- read_html(url_18) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()
r_18 <- as.data.frame(r_18)
r_18 <- r_18[(2:194),]

r_18 <- as.data.frame(r_18) %>%
  mutate(id = row_number())

t_18 <- merge(w_18,r_18,by = "id")
t_18[1] <- NULL
```
# 2017
```{r}
url_17 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif010117.htm"
w_17 <- read_html(url_17) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()
w_17 <- as.data.frame(w_17)
w_17 <- w_17[(5:197),]

w_17 <- as.data.frame(w_17) %>%
  mutate(id = row_number())
w_17$w_17 <- gsub(" [0-9]+", "",w_17$w_17)

r_17 <- read_html(url_17) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()
r_17 <- as.data.frame(r_17)
r_17 <- r_17[(2:194),]

r_17 <- as.data.frame(r_17) %>%
  mutate(id = row_number())

t_17 <- merge(w_17,r_17,by = "id")
t_17[1] <- NULL
```
# 2016
```{r}
url_16 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif010116.htm"
w_16 <- read_html(url_16) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_16 <- as.data.frame(w_16)
w_16 <- w_16[(5:195),]

w_16 <- as.data.frame(w_16) %>%
  mutate(id = row_number())
w_16$w_16 <- gsub(" [0-9]+", "",w_16$w_16)

r_16 <- read_html(url_16) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()
r_16 <- as.data.frame(r_16)
r_16 <- r_16[(2:192),]

r_16 <- as.data.frame(r_16) %>%
  mutate(id = row_number())

t_16 <- merge(w_16,r_16,by = "id")
t_16[1] <- NULL
```
# 2015
```{r}
url_15 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif010115.htm"
w_15 <- read_html(url_15) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_15 <- as.data.frame(w_15)
w_15 <- w_15[(5:195),]

w_15 <- as.data.frame(w_15) %>%
  mutate(id = row_number())
w_15$w_15 <- gsub(" [0-9]+", "",w_15$w_15)

r_15 <- read_html(url_15) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()
r_15 <- as.data.frame(r_15)
r_15 <- r_15[(2:192),]

r_15 <- as.data.frame(r_15) %>%
  mutate(id = row_number())

t_15 <- merge(w_15,r_15,by = "id")
t_15[1] <- NULL
```
# 2014
```{r}
url_14 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif010114.htm"
w_14 <- read_html(url_14) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_14 <- as.data.frame(w_14)
w_14 <- w_14[(5:193),]

w_14 <- as.data.frame(w_14) %>%
  mutate(id = row_number())
w_14$w_14 <- gsub(" [0-9]+", "",w_14$w_14)

r_14 <- read_html(url_14) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()
r_14 <- as.data.frame(r_14)
r_14 <- r_14[(2:190),]

r_14 <- as.data.frame(r_14) %>%
  mutate(id = row_number())

t_14 <- merge(w_14,r_14,by = "id")
t_14[1] <- NULL
```
# 2013
```{r}
url_13 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif010113.htm"
w_13 <- read_html(url_13) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_13 <- as.data.frame(w_13)
w_13 <- w_13[(5:194),]

w_13 <- as.data.frame(w_13) %>%
  mutate(id = row_number())
w_13$w_13 <- gsub(" [0-9]+", "",w_13$w_13)

r_13 <- read_html(url_13) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()
r_13 <- as.data.frame(r_13)
r_13 <- r_13[(2:191),]

r_13 <- as.data.frame(r_13) %>%
  mutate(id = row_number())

t_13 <- merge(w_13,r_13,by = "id")
t_13[1] <- NULL
```
# 2012
```{r}
url_12 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif310112.htm"
w_12 <- read_html(url_12) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_12 <- as.data.frame(w_12)
w_12 <- w_12[(5:193),]

w_12 <- as.data.frame(w_12) %>%
  mutate(id = row_number())
w_12$w_12 <- gsub(" [0-9]+", "",w_12$w_12)

r_12 <- read_html(url_12) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()
r_12 <- as.data.frame(r_12)
r_12 <- r_12[(2:190),]

r_12 <- as.data.frame(r_12) %>%
  mutate(id = row_number())

t_12 <- merge(w_12,r_12,by = "id")
t_12[1] <- NULL
```
# 2011
```{r}
url_11 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif310111.htm"
w_11 <- read_html(url_11) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_11 <- as.data.frame(w_11)
w_11 <- w_11[(5:192),]

w_11 <- as.data.frame(w_11) %>%
  mutate(id = row_number())
w_11$w_11 <- gsub(" [0-9]+", "",w_11$w_11)

r_11 <- read_html(url_11) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()
r_11 <- as.data.frame(r_11)
r_11 <- r_11[(2:189),]

r_11 <- as.data.frame(r_11) %>%
  mutate(id = row_number())

t_11 <- merge(w_11,r_11,by = "id")
t_11[1] <- NULL
```
# 2010
```{r}
url_10 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif310110.htm"
w_10 <- read_html(url_10) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_10 <- as.data.frame(w_10)
w_10 <- w_10[(5:191),]

w_10 <- as.data.frame(w_10) %>%
  mutate(id = row_number())
w_10$w_10 <- gsub(" [0-9]+", "",w_10$w_10)

r_10 <- read_html(url_10) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()
r_10 <- as.data.frame(r_10)
r_10 <- r_10[(2:188),]

r_10 <- as.data.frame(r_10) %>%
  mutate(id = row_number())

t_10 <- merge(w_10,r_10,by = "id")
t_10[1] <- NULL
```
# 2009
```{r}
url_9 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif310109.htm"
w_9 <- read_html(url_9) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_9 <- as.data.frame(w_9)
w_9 <- w_9[(4:191),]
w_9 <- as.data.frame(w_9) %>%
        mutate(id = row_number())
w_9$w_9 <- gsub(" [0-9]+", "",w_9$w_9)

r_9 <- read_html(url_9) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()

r_9 <- as.data.frame(r_9)
r_9 <- r_9[(2:189),]
r_9 <- as.data.frame(r_9) %>%
        mutate(id = row_number())

t_9<- merge(w_9, r_9, by = "id")
t_9[1] <- NULL
```
# 2008
```{r}
url_8 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif310108.htm"

w_8 <- read_html(url_8) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_8 <- as.data.frame(w_8)
w_8 <- w_8[(4:191),]
w_8 <- as.data.frame(w_8) %>%
        mutate(id = row_number())
w_8$w_8 <- gsub(" [0-9]+", "",w_8$w_8)

r_8 <- read_html(url_8) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()

r_8 <- as.data.frame(r_8)
r_8 <- r_8[(2:189),]
r_8 <- as.data.frame(r_8) %>%
        mutate(id = row_number())

t_8<- merge(w_8, r_8, by = "id")
t_8[1] <- NULL
```
# 2007
```{r}
url_7 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif310107.htm"

w_7 <- read_html(url_7) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_7 <- as.data.frame(w_7)
w_7 <- w_7[(4:192),]
w_7 <- as.data.frame(w_7) %>%
        mutate(id = row_number())
w_7$w_7 <- gsub(" [0-9]+", "",w_7$w_7)

r_7 <- read_html(url_7) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()

r_7 <- as.data.frame(r_7)
r_7 <- r_7[(2:190),]
r_7 <- as.data.frame(r_7) %>%
        mutate(id = row_number())

t_7<- merge(w_7, r_7, by = "id")
t_7[1] <- NULL
```
# 2006
```{r}
url_6 <- "http://web.archive.org/web/20190315152617/http://archive.ipu.org/wmn-e/arc/classif310106.htm"

w_6 <- read_html(url_6) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_6 <- as.data.frame(w_6)
w_6 <- w_6[(4:190),]
w_6 <- as.data.frame(w_6) %>%
        mutate(id = row_number())
w_6$w_6 <- gsub(" [0-9]+", "",w_6$w_6)

r_6 <- read_html(url_6) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()

r_6 <- as.data.frame(r_6)
r_6 <- r_6[(2:188),]
r_6 <- as.data.frame(r_6) %>%
        mutate(id = row_number())

t_6<- merge(w_6, r_6, by = "id")
t_6[1] <- NULL
```
# 2005
```{r}
url_5 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif310105.htm"

w_5 <- read_html(url_5) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_5 <- as.data.frame(w_5)
w_5 <- w_5[(4:187),]
w_5 <- as.data.frame(w_5) %>%
        mutate(id = row_number())
w_5$w_5 <- gsub(" [0-9]+", "",w_5$w_5)

r_5 <- read_html(url_5) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()

r_5 <- as.data.frame(r_5)
r_5 <- r_5[(2:185),]
r_5 <- as.data.frame(r_5) %>%
        mutate(id = row_number())

t_5<- merge(w_5, r_5, by = "id")
t_5[1] <- NULL
```
# 2004
```{r}
url_4 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif300104.htm"

w_4 <- read_html(url_4) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_4 <- as.data.frame(w_4)
w_4 <- w_4[(4:184),]
w_4 <- as.data.frame(w_4) %>%
        mutate(id = row_number())
w_4$w_4 <- gsub(" [0-9]+", "",w_4$w_4)

r_4 <- read_html(url_4) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()

r_4 <- as.data.frame(r_4)
r_4 <- r_4[(2:182),]
r_4 <- as.data.frame(r_4) %>%
        mutate(id = row_number())

t_4<- merge(w_4, r_4, by = "id")
t_4[1] <- NULL
```
# 2003
```{r}
url_3 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif310103.htm"

w_3 <- read_html(url_3) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_3 <- as.data.frame(w_3)
w_3 <- w_3[(4:185),]
w_3 <- as.data.frame(w_3) %>%
        mutate(id = row_number())
w_3$w_3 <- gsub(" [0-9]+", "",w_3$w_3)

r_3 <- read_html(url_3) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()

r_3 <- as.data.frame(r_3)
r_3 <- r_3[(2:183),]
r_3 <- as.data.frame(r_3) %>%
        mutate(id = row_number())

t_3<- merge(w_3, r_3, by = "id")
t_3[1] <- NULL
```
# 2002
```{r}
url_2 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif040202.htm"

w_2 <- read_html(url_2) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_2 <- as.data.frame(w_2)
w_2 <- w_2[(4:182),]
w_2 <- as.data.frame(w_2) %>%
        mutate(id = row_number())
w_2$w_2 <- gsub(" [0-9]+", "",w_2$w_2)

r_2 <- read_html(url_2) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()

r_2 <- as.data.frame(r_2)
r_2 <- r_2[(2:180),]
r_2 <- as.data.frame(r_2) %>%
        mutate(id = row_number())

t_2<- merge(w_2, r_2, by = "id")
t_2[1] <- NULL
```
# 2001
```{r}
url_1 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif300101.htm"

w_1 <- read_html(url_1) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_1 <- as.data.frame(w_1)
w_1 <- w_1[(4:181),]
w_1 <- as.data.frame(w_1) %>%
        mutate(id = row_number())
w_1$w_1 <- gsub(" [0-9]+", "",w_1$w_1)

r_1 <- read_html(url_1) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()

r_1 <- as.data.frame(r_1)
r_1 <- r_1[(2:179),]
r_1 <- as.data.frame(r_1) %>%
        mutate(id = row_number())

t_1<- merge(w_1, r_1, by = "id")
t_1[1] <- NULL
```
# 2000
```{r}
url_0 <- "http://webcache.googleusercontent.com/search?q=cache:http://archive.ipu.org/wmn-e/arc/classif250100.htm"

w_0 <- read_html(url_0) %>%
  html_nodes("td:nth-child(2)") %>%
  html_text()

w_0 <- as.data.frame(w_0)
w_0 <- w_0[(4:180),]
w_0 <- as.data.frame(w_0) %>%
        mutate(id = row_number())
w_0$w_0 <- gsub(" [0-9]+", "",w_0$w_0)

r_0 <- read_html(url_0) %>%
  html_nodes("td:nth-child(6)") %>%
  html_text()

r_0 <- as.data.frame(r_0)
r_0 <- r_0[(2:178),]
r_0 <- as.data.frame(r_0) %>%
        mutate(id = row_number())

t_0<- merge(w_0, r_0, by = "id")
t_0[1] <- NULL

```


#Joining Data
```{r}
# Joining data of 2019-2010
t_all <- t_19 %>%  left_join(t_18, by = c("w_19" = "w_18")) %>%
         left_join(t_17, by = c("w_19" = "w_17")) %>%
         left_join(t_16, by = c("w_19" = "w_16")) %>%
         left_join(t_15, by = c("w_19" = "w_15")) %>%
         left_join(t_14, by = c("w_19" = "w_14")) %>%
         left_join(t_13, by = c("w_19" = "w_13")) %>%
         left_join(t_12, by = c("w_19" = "w_12")) %>%
         left_join(t_11, by = c("w_19" = "w_11")) %>%
         left_join(t_10, by = c("w_19" = "w_10")) %>%
         left_join(t_9, by = c("w_19" = "w_9")) %>%
         left_join(t_8, by = c("w_19" = "w_8")) %>%
         left_join(t_7, by = c("w_19" = "w_7")) %>%
         left_join(t_6, by = c("w_19" = "w_6")) %>%
         left_join(t_5, by = c("w_19" = "w_5")) %>%
         left_join(t_4, by = c("w_19" = "w_4")) %>%
         left_join(t_3, by = c("w_19" = "w_3")) %>%
         left_join(t_2, by = c("w_19" = "w_2")) %>%
         left_join(t_1, by = c("w_19" = "w_1")) %>%
         left_join(t_0, by = c("w_19" = "w_0")) 
```

#Cleaning Data
```{r}
# Remove "%"
t_all$r_8 <- gsub("%", "",t_all$r_8)
t_all$r_9 <- gsub("%", "",t_all$r_9)
t_all$r_10 <- gsub("%", "",t_all$r_10)
t_all$r_11 <- gsub("%", "",t_all$r_11)
t_all$r_12 <- gsub("%", "",t_all$r_12)
t_all$r_13 <- gsub("%", "",t_all$r_13)
t_all$r_14 <- gsub("%", "",t_all$r_14)
t_all$r_15 <- gsub("%", "",t_all$r_15)
t_all$r_16 <- gsub("%", "",t_all$r_16)
t_all$r_17 <- gsub("%", "",t_all$r_17)
t_all$r_18 <- gsub("%", "",t_all$r_18)
t_all$r_19 <- gsub("%", "",t_all$r_19)

# Replace "?" 

t_all$r_0 <- gsub("\\?", "0",t_all$r_0)
t_all$r_1 <- gsub("\\?", "0",t_all$r_1)
t_all$r_2 <- gsub("\\?", "0",t_all$r_2)
t_all$r_3 <- gsub("\\?", "0",t_all$r_3)
t_all$r_4 <- gsub("\\?", "0",t_all$r_4)
t_all$r_5 <- gsub("\\?", "0",t_all$r_5)
t_all$r_6 <- gsub("\\?", "0",t_all$r_6)
t_all$r_7 <- gsub("\\?", "0",t_all$r_7)
t_all$r_8 <- gsub("\\?", "0",t_all$r_8)
t_all$r_9 <- gsub("\\?", "0",t_all$r_9)
t_all$r_10 <- gsub("\\?", "0",t_all$r_10)
t_all$r_11 <- gsub("\\?", "0",t_all$r_11)
t_all$r_12 <- gsub("\\?", "0",t_all$r_12)

# t_all$r_0 <- gsub("\\?", "NA",t_all$r_0)
# t_all$r_1 <- gsub("\\?", "NA",t_all$r_1)
# t_all$r_2 <- gsub("\\?", "NA",t_all$r_2)
# t_all$r_3 <- gsub("\\?", "NA",t_all$r_3)
# t_all$r_4 <- gsub("\\?", "NA",t_all$r_4)
# t_all$r_5 <- gsub("\\?", "NA",t_all$r_5)
# t_all$r_6 <- gsub("\\?", "NA",t_all$r_6)
# t_all$r_7 <- gsub("\\?", "NA",t_all$r_7)
# t_all$r_8 <- gsub("\\?", "NA",t_all$r_8)
# t_all$r_9 <- gsub("\\?", "NA",t_all$r_9)
# t_all$r_10 <- gsub("\\?", "NA",t_all$r_10)
# t_all$r_11 <- gsub("\\?", "NA",t_all$r_11)
# t_all$r_12 <- gsub("\\?", "NA",t_all$r_12)

# t_all$r_0 <- gsub("NA", "0",t_all$r_0)
# t_all$r_1 <- gsub("NA", "0",t_all$r_1)
# t_all$r_2 <- gsub("NA", "0",t_all$r_2)
# t_all$r_3 <- gsub("NA", "0",t_all$r_3)
# t_all$r_4 <- gsub("NA", "0",t_all$r_4)
# t_all$r_5 <- gsub("NA", "0",t_all$r_5)
# t_all$r_6 <- gsub("NA", "0",t_all$r_6)
# t_all$r_7 <- gsub("NA", "0",t_all$r_7)
# t_all$r_8 <- gsub("NA", "0",t_all$r_8)
# t_all$r_9 <- gsub("NA", "0",t_all$r_9)
# t_all$r_10 <- gsub("NA", "0",t_all$r_10)
# t_all$r_11 <- gsub("NA", "0",t_all$r_11)
# t_all$r_12 <- gsub("NA", "0",t_all$r_12)

# Replace "NA"
t_all[is.na(t_all)] <- -0

# Replace "," to "."
t_all$r_19 <- gsub(",", ".",t_all$r_19)
```

#Download data csv
```{r}
write.csv(t_all,"/Users/sunchiachun/Documents/作業/1082新聞資料處理與視覺呈現/Final report/t_all_2.csv", row.names = FALSE)

write.csv(t_all,"/Users/sunchiachun/Documents/作業/1082新聞資料處理與視覺呈現/Final report/t_all_withNA.csv", row.names = FALSE)

```



#Categorizing Data:2019
```{r} 
# Duplicate a dataframe
t_level <-data.frame(t_all)

# Convert data class to numeric

# Categorizing data
for (i in 1:nrow(t_all)){
  if (t_all$r_19[i] >= 50 & t_all$r_19[i] < 70){
    t_level$r_19[i] <- 6
  } else if (t_all$r_19[i] >= 40 & t_all$r_19[i] < 50){
    t_level$r_19[i] <- 5
  } else if (t_all$r_19[i] >= 30 & t_all$r_19[i] < 40){
    t_level$r_19[i] <- 4
  } else if (t_all$r_19[i] >= 20 & t_all$r_19[i] < 30){
    t_level$r_19[i] <- 3
  } else if (t_all$r_19[i] >= 10 & t_all$r_19[i] < 20){
    t_level$r_19[i] <- 2
  # } else if (t_all$r_19[i] < 0){
  #   t_level$r_19[i] <- 0    
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}


# as.data.frame(
#   lapply(
#     t_all, 
#     function(col) 
#       if(is.numeric(col)) {col + 1} else {col}))
#         if (col >= 50 & col < 70){
#           t_level[i,j] <- 6
#         } else if (t_all[i,j] >= 40 & t_all[i,j] < 50){
#           t_level[i,j] <- 5
#         } else if (t_all[i,j] >= 30 & t_all[i,j] < 40){
#           t_level[i,j] <- 4
#         } else if (t_all[i,j] >= 20 & t_all[i,j] < 30){
#           t_level[i,j] <- 3
#         } else if (t_all[i,j] >= 10 & t_all[i,j] < 20){
#           t_level[i,j] <- 2
#         # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
#         #   t_level$r_19[i] <- 1
#        }
#       }
#       }
# 

# for (i in 1:nrow(t_all[i]))
#   {
#    for(j in 2:ncol(t_all[j])){
#   if (t_all[i,j] >= 50 & t_all[i,j] < 70){
#     t_level[i,j] <- 6
#   } else if (t_all[i,j] >= 40 & t_all[i,j] < 50){
#     t_level[i,j] <- 5
#   } else if (t_all[i,j] >= 30 & t_all[i,j] < 40){
#     t_level[i,j] <- 4
#   } else if (t_all[i,j] >= 20 & t_all[i,j] < 30){
#     t_level[i,j] <- 3
#   } else if (t_all[i,j] >= 10 & t_all[i,j] < 20){
#     t_level[i,j] <- 2
#   # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
#   #   t_level$r_19[i] <- 1
#  }
# }
# }

# t_all$r_19 <- ifelse(t_all$r_19<=10, 1, )
# 
# as.numeric(unlist(t_all[,2:21]))
# class()
# 
#   for (i in 1:nrow(t_all)){
# 	  if (t_all$r_19[i] <= 10){
# 	      t_all$r_19[i] = 1}
# 	}
#     
#   for(i in 1:nrow(df)){
#     if(df$var[i]==" ?"){
#         df$var[i]="Private"
#      }
# }  
    
# frame$twohouses <- ifelse(frame$data>=2, 2, 1)
  
```
#Categorizing Data: 2018
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_18[i] >= 50 & t_all$r_18[i] < 70){
    t_level$r_18[i] <- 6
  } else if (t_all$r_18[i] >= 40 & t_all$r_18[i] < 50){
    t_level$r_18[i] <- 5
  } else if (t_all$r_18[i] >= 30 & t_all$r_18[i] < 40){
    t_level$r_18[i] <- 4
  } else if (t_all$r_18[i] >= 20 & t_all$r_18[i] < 30){
    t_level$r_18[i] <- 3
  } else if (t_all$r_18[i] >= 10 & t_all$r_18[i] < 20){
    t_level$r_18[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2017
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_17[i] >= 50 & t_all$r_17[i] < 70){
    t_level$r_17[i] <- 6
  } else if (t_all$r_17[i] >= 40 & t_all$r_17[i] < 50){
    t_level$r_17[i] <- 5
  } else if (t_all$r_17[i] >= 30 & t_all$r_17[i] < 40){
    t_level$r_17[i] <- 4
  } else if (t_all$r_17[i] >= 20 & t_all$r_17[i] < 30){
    t_level$r_17[i] <- 3
  } else if (t_all$r_17[i] >= 10 & t_all$r_17[i] < 20){
    t_level$r_17[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```

#Categorizing Data: 2016
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_16[i] >= 50 & t_all$r_16[i] < 70){
    t_level$r_16[i] <- 6
  } else if (t_all$r_16[i] >= 40 & t_all$r_16[i] < 50){
    t_level$r_16[i] <- 5
  } else if (t_all$r_16[i] >= 30 & t_all$r_16[i] < 40){
    t_level$r_16[i] <- 4
  } else if (t_all$r_16[i] >= 20 & t_all$r_16[i] < 30){
    t_level$r_16[i] <- 3
  } else if (t_all$r_16[i] >= 10 & t_all$r_16[i] < 20){
    t_level$r_16[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2015
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_15[i] >= 50 & t_all$r_15[i] < 70){
    t_level$r_15[i] <- 6
  } else if (t_all$r_15[i] >= 40 & t_all$r_15[i] < 50){
    t_level$r_15[i] <- 5
  } else if (t_all$r_15[i] >= 30 & t_all$r_15[i] < 40){
    t_level$r_15[i] <- 4
  } else if (t_all$r_15[i] >= 20 & t_all$r_15[i] < 30){
    t_level$r_15[i] <- 3
  } else if (t_all$r_15[i] >= 10 & t_all$r_15[i] < 20){
    t_level$r_15[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2014
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_14[i] >= 50 & t_all$r_14[i] < 70){
    t_level$r_14[i] <- 6
  } else if (t_all$r_14[i] >= 40 & t_all$r_14[i] < 50){
    t_level$r_14[i] <- 5
  } else if (t_all$r_14[i] >= 30 & t_all$r_14[i] < 40){
    t_level$r_14[i] <- 4
  } else if (t_all$r_14[i] >= 20 & t_all$r_14[i] < 30){
    t_level$r_14[i] <- 3
  } else if (t_all$r_14[i] >= 10 & t_all$r_14[i] < 20){
    t_level$r_14[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2013
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_13[i] >= 50 & t_all$r_13[i] < 70){
    t_level$r_13[i] <- 6
  } else if (t_all$r_13[i] >= 40 & t_all$r_13[i] < 50){
    t_level$r_13[i] <- 5
  } else if (t_all$r_13[i] >= 30 & t_all$r_13[i] < 40){
    t_level$r_13[i] <- 4
  } else if (t_all$r_13[i] >= 20 & t_all$r_13[i] < 30){
    t_level$r_13[i] <- 3
  } else if (t_all$r_13[i] >= 10 & t_all$r_13[i] < 20){
    t_level$r_13[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2012
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_12[i] >= 50 & t_all$r_12[i] < 70){
    t_level$r_12[i] <- 6
  } else if (t_all$r_12[i] >= 40 & t_all$r_12[i] < 50){
    t_level$r_12[i] <- 5
  } else if (t_all$r_12[i] >= 30 & t_all$r_12[i] < 40){
    t_level$r_12[i] <- 4
  } else if (t_all$r_12[i] >= 20 & t_all$r_12[i] < 30){
    t_level$r_12[i] <- 3
  } else if (t_all$r_12[i] >= 10 & t_all$r_12[i] < 20){
    t_level$r_12[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2011
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_11[i] >= 50 & t_all$r_11[i] < 70){
    t_level$r_11[i] <- 6
  } else if (t_all$r_11[i] >= 40 & t_all$r_11[i] < 50){
    t_level$r_11[i] <- 5
  } else if (t_all$r_11[i] >= 30 & t_all$r_11[i] < 40){
    t_level$r_11[i] <- 4
  } else if (t_all$r_11[i] >= 20 & t_all$r_11[i] < 30){
    t_level$r_11[i] <- 3
  } else if (t_all$r_11[i] >= 10 & t_all$r_11[i] < 20){
    t_level$r_11[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2010
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_10[i] >= 50 & t_all$r_10[i] < 70){
    t_level$r_10[i] <- 6
  } else if (t_all$r_10[i] >= 40 & t_all$r_10[i] < 50){
    t_level$r_10[i] <- 5
  } else if (t_all$r_10[i] >= 30 & t_all$r_10[i] < 40){
    t_level$r_10[i] <- 4
  } else if (t_all$r_10[i] >= 20 & t_all$r_10[i] < 30){
    t_level$r_10[i] <- 3
  } else if (t_all$r_10[i] >= 10 & t_all$r_10[i] < 20){
    t_level$r_10[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2009
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_9[i] >= 50 & t_all$r_9[i] < 70){
    t_level$r_9[i] <- 6
  } else if (t_all$r_9[i] >= 40 & t_all$r_9[i] < 50){
    t_level$r_9[i] <- 5
  } else if (t_all$r_9[i] >= 30 & t_all$r_9[i] < 40){
    t_level$r_9[i] <- 4
  } else if (t_all$r_9[i] >= 20 & t_all$r_9[i] < 30){
    t_level$r_9[i] <- 3
  } else if (t_all$r_9[i] >= 10 & t_all$r_9[i] < 20){
    t_level$r_9[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2008
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_8[i] >= 50 & t_all$r_8[i] < 70){
    t_level$r_8[i] <- 6
  } else if (t_all$r_8[i] >= 40 & t_all$r_8[i] < 50){
    t_level$r_8[i] <- 5
  } else if (t_all$r_8[i] >= 30 & t_all$r_8[i] < 40){
    t_level$r_8[i] <- 4
  } else if (t_all$r_8[i] >= 20 & t_all$r_8[i] < 30){
    t_level$r_8[i] <- 3
  } else if (t_all$r_8[i] >= 10 & t_all$r_8[i] < 20){
    t_level$r_8[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2007
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_7[i] >= 50 & t_all$r_7[i] < 70){
    t_level$r_7[i] <- 6
  } else if (t_all$r_7[i] >= 40 & t_all$r_7[i] < 50){
    t_level$r_7[i] <- 5
  } else if (t_all$r_7[i] >= 30 & t_all$r_7[i] < 40){
    t_level$r_7[i] <- 4
  } else if (t_all$r_7[i] >= 20 & t_all$r_7[i] < 30){
    t_level$r_7[i] <- 3
  } else if (t_all$r_7[i] >= 10 & t_all$r_7[i] < 20){
    t_level$r_7[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2006
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_6[i] >= 50 & t_all$r_6[i] < 70){
    t_level$r_6[i] <- 6
  } else if (t_all$r_6[i] >= 40 & t_all$r_6[i] < 50){
    t_level$r_6[i] <- 5
  } else if (t_all$r_6[i] >= 30 & t_all$r_6[i] < 40){
    t_level$r_6[i] <- 4
  } else if (t_all$r_6[i] >= 20 & t_all$r_6[i] < 30){
    t_level$r_6[i] <- 3
  } else if (t_all$r_6[i] >= 10 & t_all$r_6[i] < 20){
    t_level$r_6[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2005
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_5[i] >= 50 & t_all$r_5[i] < 70){
    t_level$r_5[i] <- 6
  } else if (t_all$r_5[i] >= 40 & t_all$r_5[i] < 50){
    t_level$r_5[i] <- 5
  } else if (t_all$r_5[i] >= 30 & t_all$r_5[i] < 40){
    t_level$r_5[i] <- 4
  } else if (t_all$r_5[i] >= 20 & t_all$r_5[i] < 30){
    t_level$r_5[i] <- 3
  } else if (t_all$r_5[i] >= 10 & t_all$r_5[i] < 20){
    t_level$r_5[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2004
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_4[i] >= 50 & t_all$r_4[i] < 70){
    t_level$r_4[i] <- 6
  } else if (t_all$r_4[i] >= 40 & t_all$r_4[i] < 50){
    t_level$r_4[i] <- 5
  } else if (t_all$r_4[i] >= 30 & t_all$r_4[i] < 40){
    t_level$r_4[i] <- 4
  } else if (t_all$r_4[i] >= 20 & t_all$r_4[i] < 30){
    t_level$r_4[i] <- 3
  } else if (t_all$r_4[i] >= 10 & t_all$r_4[i] < 20){
    t_level$r_4[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2003
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_3[i] >= 50 & t_all$r_3[i] < 70){
    t_level$r_3[i] <- 6
  } else if (t_all$r_3[i] >= 40 & t_all$r_3[i] < 50){
    t_level$r_3[i] <- 5
  } else if (t_all$r_3[i] >= 30 & t_all$r_3[i] < 40){
    t_level$r_3[i] <- 4
  } else if (t_all$r_3[i] >= 20 & t_all$r_3[i] < 30){
    t_level$r_3[i] <- 3
  } else if (t_all$r_3[i] >= 10 & t_all$r_3[i] < 20){
    t_level$r_3[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2002
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_2[i] >= 50 & t_all$r_2[i] < 70){
    t_level$r_2[i] <- 6
  } else if (t_all$r_2[i] >= 40 & t_all$r_2[i] < 50){
    t_level$r_2[i] <- 5
  } else if (t_all$r_2[i] >= 30 & t_all$r_2[i] < 40){
    t_level$r_2[i] <- 4
  } else if (t_all$r_2[i] >= 20 & t_all$r_2[i] < 30){
    t_level$r_2[i] <- 3
  } else if (t_all$r_2[i] >= 10 & t_all$r_2[i] < 20){
    t_level$r_2[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2001
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_1[i] >= 50 & t_all$r_1[i] < 70){
    t_level$r_1[i] <- 6
  } else if (t_all$r_1[i] >= 40 & t_all$r_1[i] < 50){
    t_level$r_1[i] <- 5
  } else if (t_all$r_1[i] >= 30 & t_all$r_1[i] < 40){
    t_level$r_1[i] <- 4
  } else if (t_all$r_1[i] >= 20 & t_all$r_1[i] < 30){
    t_level$r_1[i] <- 3
  } else if (t_all$r_1[i] >= 10 & t_all$r_1[i] < 20){
    t_level$r_1[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Categorizing Data: 2000
```{r}
for (i in 1:nrow(t_all)){
  if (t_all$r_0[i] >= 50 & t_all$r_0[i] < 70){
    t_level$r_0[i] <- 6
  } else if (t_all$r_0[i] >= 40 & t_all$r_0[i] < 50){
    t_level$r_0[i] <- 5
  } else if (t_all$r_0[i] >= 30 & t_all$r_0[i] < 40){
    t_level$r_0[i] <- 4
  } else if (t_all$r_0[i] >= 20 & t_all$r_0[i] < 30){
    t_level$r_0[i] <- 3
  } else if (t_all$r_0[i] >= 10 & t_all$r_0[i] < 20){
    t_level$r_0[i] <- 2
  # } else if (t_all$r_19[i] >= 0 & t_all$r_19[i] < 10){
  #   t_level$r_19[i] <- 1
 }
}
```
#Download data csv
```{r}
write.csv(t_level,"/Users/sunchiachun/Documents/作業/1082新聞資料處理與視覺呈現/Final report/t_level_unchecked.csv", row.names = FALSE)
```

#Import checked data csv
```{r}
t_level2 <- read.csv("/Users/sunchiachun/Documents/作業/1082新聞資料處理與視覺呈現/Final report/t_level_checked.csv")

#Adjust the dataframe

names(t_level2)[2:11] = gsub(pattern = "r_", replacement = "20", x = names(t_level2)[2:11])
names(t_level2)[12:21] = gsub(pattern = "r_", replacement = "200", x = names(t_level2)[12:21])

t_level2 <- t_level2[,sort(names(t_level2))]
t_level2 <- t_level2 %>%
  select(w_19, everything())
names(t_level2)[1] <- paste("country")
```

#Plotting: barplot
```{r}
#Test: plotting one country
barplot(unlist(t_level2[2, -1]), space = 0, border = NA, 
        xaxt = "n", yaxt ="n", main = t_level2[2, 1], line = -4, 
        cex.main = 5, ylim = c(0,5 ))


#Subset different groups 

g5 <- t_level2[t_level2$`2019` >= 5,]
g4 <- t_level2[t_level2$`2019` == 4,]
g3 <- t_level2[t_level2$`2019` == 3,]

#Use for-loop to plot multiple lines 
par(mfrow = c(4,6), mar = c(0, 0, 0, 0) + 0.2)
for(i in 1:nrow(g5)){
barplot(unlist(g5[i, -1]), space = 0, border = NA, 
        xaxt = "n", yaxt ="n", 
        main = g5[i, 1], line = -3, cex.main = 1.5, 
        ylim = c(0,5))
}
```
# Plotting: ggplot2
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readxl)

g5 %>%
	gather("year", "degree", 2:21) %>%
	replace_na(list(degree=0)) %>%
	ggplot() +
	aes(year, degree) +
    geom_col(color="royalblue", fill="royalblue") + 
	facet_wrap(~ country) + 
  theme_void() 
  # scale_x_discrete()



# g5 %>%
# 	gather("year", "degree", 2:21) %>%
# 	replace_na(list(degree=0)) %>%
# 	ggplot() +
# 	aes(year, degree) +
#     geom_col(color="royalblue", fill="royalblue") + 
# 	facet_wrap(~ country) + 
#     theme_class() 

# par(mfrow = c(4,6), mar = c(0, 0, 0, 0) + 0.2)
# for(i in 1:nrow(g5)){
# barplot(unlist(g5[i, -1]), space = 0, border = NA, 
#         xaxt = "n", yaxt ="n", 
#         main = g5[i, 1], line = -3, cex.main = 1.5, 
#         ylim = c(0,5))
# }


```

# Human Development Index
```{r}
url_hdi <- "https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index"
hdi_country <- read_html(url_hdi) %>%
  html_nodes("td:nth-child(3) > a") %>%
  html_text()
hdi_country <- as.data.frame(hdi_country)%>%
  mutate(id = row_number())

hdi_19 <- read_html(url_hdi) %>%
  html_nodes("td:nth-child(4)") %>%
  html_text()
hdi_19 <- as.data.frame(hdi_19)
hdi_19  <- hdi_19 [(1:190),]
hdi_19 <- as.data.frame(hdi_19)
hdi_19 <- hdi_19 [-93,] %>%
  as.data.frame(hdi_19) %>%
  mutate(id = row_number())

hdi_rank <- merge(hdi_country, hdi_19, by = "id")
hdi_rank[1] <- NULL

names(hdi_rank)[1]<-"country_name"


```

```{r}
# t_all <- t_19 %>%  left_join(t_18, by = c("w_19" = "w_18")) %>%
#          left_join(t_17, by = c("w_19" = "w_17")) %>%

hdi <- t_19 %>%  left_join(hdi_rank, by = c("w_19" = "country_name"))
write.csv(hdi,"hdi.csv", row.names = FALSE)
```

# Save rda
```{r}

all_data <- t_all_withNA %>%  left_join(hdi_rank, by = c("w_19" = "country_name"))
write.csv(all_data,"all_data.csv", row.names = FALSE)

data <- read.csv("all_data - all_data.csv")
save(data, file="women in parliament.rda")


```


